BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-14 tex/4-techniques.tex
Techniques done.

Our use case has two types of spiders: NewCrawl and UpdateCrawl, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download images
  \item Propagate resulting records to the Invenio backend
\end{enumerate}
This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative backend can be done by editing a single configuration line.

@@

\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable.

{{If one of these layers does not participate—making blocking calls to the database, relying on shared mutable state, calling out to expensive synchronous operations—then the whole pipeline stalls and users will suffer through increased latency and reduced scalability.}}\cite{reactivemanifesto2013}

At the time of writting we did not had the chance to work on a distributed depoyement of the BlogForever project. However, the crawler was built tu be

Scrapy is written with Twisted, a popular event-driven networking framework for Python. Thus, it’s implemented using a non-blocking (aka asynchronous) code for concurrency.

Scrapy uses the Twisted\cite{twisted2013} asynchronous networking engine

At the time of writing...
- http://www.reactivemanifesto.org/
- stateless \\
- scrapyd \\

>>>>

Our use case has two types of spiders: \emph{NewCrawl} and \emph{UpdateCrawl}, which respectively implement the logic to crawl a new blog and to get updates from a previously crawled blog. After downloading the HTML page, blog posts are packed into Items and sent through the folloing pipeline of operation:
\begin{enumerate}[noitemsep]
  \item Render JavaScript
  \item Extract content
  \item Extract comments
  \item Download images
  \item Propagate resulting records to the Invenio backend
\end{enumerate}
This pipeline design, often called the \emph{pipes and filters pattern}\cite[Chapter Messaging Systems]{hohpe2003}, provides great modularity. Indeed, disabeling JavaScript rendering or plugging in an alternative backend can be done by editing a single configuration line.

@@

\subsection{Scalability}
When aiming to work with a large number of inputs, it is crucial that every layer of the system is build to be scalable. Citing the Reactive Manifesto\cite{thereactivemanifesto2013}:

\begin{quoting}
  If one of these layers does not participate—making blocking calls to the database, relying on shared mutable state, calling out to expensive synchronous operations—then the whole pipeline stalls and users will suffer through increased latency and reduced scalability.
\end{quoting}

At the time of writing we did not had the chance to work on a distributed deployment of the BlogForever project. However, the BlogForever crawler, and in particular the two core procedures \emph{NewCrawl} and \emph{UpdateCrawl}, where designed to be usable as part of a event-driven, scalable and fault resilient distributed system.

\Anotecontent{commentfeed}{Blogs that do not provide a global comment feed need a special handling. If comment feeds are attached to each blog post, periodically checking for comment updates might be done with a reasonable cost. However, in the worst case where no comment feeds are provided, the only solution is to periodically do a full crawl of the blog to capture new comments.}

Scalability and fault resilience are induced by the fact that both \emph{NewCrawl} and \emph{UpdateCrawl} are from a high level viewpoint stateless entities. \emph{NewCrawl} can be seen as a function, which takes as input the URL of a blog and returns structured records for blog-posts, comments and medias. Similarly, \emph{UpdateCrawl} takes as inputs the URL of blog\Anote{commentfeed} and a time, and returns records of objects that where emitted after the given time. The absence of state implies that in a distributed setup, crawler instances could be removed, added, and used interchangeably. Regarding the asynchronous architecture, Scrapy is build upon Twisted\cite{twisted2013}, an event-driven networking framework for Python. Scrapy also provides a built-in service to start spiders with an HTTP JSON API. With these tools in hand, the only component to implement in order to achieve a scalable and fault resilient distributed crawling system is an entity to keep track of available crawlers and does appropriate load balancing between them.
